Four decades of water quality change in the upper San Francisco Estuary\footnote{Version: Thu Feb 9 09:38:49 2017 -0600, \href{https://github.com/fawda123/sftrends_manu/commit/dc55a82ecaa6c7579c80e824377410a6b61dc53f}{dc55a82ecaa6c7579c80e824377410a6b61dc53f}}

### 2017-03-15 sftrends_manu.tex
recompile draft

% get online bib file
\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in curl::curl\_fetch\_memory(url, handle = handle): Timeout was reached}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in rawToChar(refs\$content): object 'refs' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in writeLines(refs, con = file("{}refs.bib"{})): object 'refs' not found}}\end{kframe}

@@

\title[Water quality change in the upper SFE]{Four decades of water quality change in the upper San Francisco Estuary\footnote{Version: Thu Mar 9 13:51:29 2017 -0600, \href{https://github.com/fawda123/sftrends_manu/commit/3a2258283f79a8ff3710c96c42f090e653e0a955}{3a2258283f79a8ff3710c96c42f090e653e0a955}\newline The views expressed in this paper are those of the authors and do not necessarily reflect the views or policies of the U.S. Environmental Protection Agency.}}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\linenumbers

>>>>

% get online bib file

@@

\title[Water quality change in the upper SFE]{Four decades of water quality change in the upper San Francisco Estuary\footnote{Version: Tue Mar 14 09:11:12 2017 -0500, \href{https://github.com/fawda123/sftrends_manu/commit/7b5a17c006b01d83e6f284649e548d329f7ada14}{7b5a17c006b01d83e6f284649e548d329f7ada14}\newline The views expressed in this paper are those of the authors and do not necessarily reflect the views or policies of the U.S. Environmental Protection Agency.}}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\linenumbers
